Comparing Results with Mafessoni et al.

### 2019-07-12 PlottingScripts/ProcessedData/ScoopCheck.Rmd
updated figure

plt <- ggplot(data, 
              aes(x = End, 
                  y = Start, 
                  fill = Freq)) +
    geom_tile() +
    facet_grid(.~Mut) +
    labs(y = name) +
    theme_classic() +
    theme(axis.title.x = element_blank(),
          axis.line = element_blank(),
          axis.text = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          strip.placement = "outside",
          strip.background = element_blank(),
          strip.text = element_text(size = 20),
          legend.text = element_text(size = 20),
          legend.title = element_text(size = 20),
          panel.border = element_rect(colour = "black", 
                                      fill = NA, 
                                      size = 1),
          plot.margin = unit(c(0,0,0,1.5), "lines")) +
    scale_fill_gradient(limits = c(0, maxFreq),
                        low = 'white', 
                        high = 'black',
                        guide = guide_legend(title = 'Variant\ncount',
                                             direction = 'vertical'))
return(plt)
}
```

@@

merged_regression_unmasked$strict_mask <- paste0("Pass strict mask (",nrow(merged_regression_unmasked),")")
merged_regression_masked$strict_mask <- paste0("Fail strict mask (",nrow(merged_regression_masked),")")

@@

to_plot <- merged_regression %>%
           filter(pvalue_glm_filt < 1 | Adjusted_Log10p > 2)

@@

p_comp
```
```{r}
#missing in Mafessoni
p <- to_plot %>%
  filter(strict_mask == 'Pass strict mask')

m_maf <- p %>%
           filter(pvalue_glm_filt == 1 & Adjusted_Log10p > 2)

#missing in ours
m_us <- p %>%
           filter(pvalue_glm_filt < 1 & Adjusted_Log10p < 2)

#present in both
both <- p %>%
           filter(pvalue_glm_filt < 1 & Adjusted_Log10p > 2)

@@

#missing in Mafessoni
f <- to_plot %>%
  filter(strict_mask == 'Fail strict mask')

m_maf <- f %>%
           filter(pvalue_glm_filt == 1 & Adjusted_Log10p > 2)

#missing in ours
m_us <- f %>%
           filter(pvalue_glm_filt < 1 & Adjusted_Log10p < 2)

#present in both
both <- f %>%
           filter(pvalue_glm_filt < 1 & Adjusted_Log10p > 2)

@@

m_maf <- to_plot %>%
           filter(pvalue_glm_filt == 1 & Adjusted_Log10p > 2)

#missing in ours
m_us <- to_plot %>%
           filter(pvalue_glm_filt < 1 & Adjusted_Log10p < 2)

#present in both
both <- to_plot %>%
           filter(pvalue_glm_filt < 1 & Adjusted_Log10p > 2)

>>>>

plt <- ggplot(data, 
              aes(x = End, 
                  y = Start, 
                  fill = Freq)) +
    geom_tile() +
    facet_grid(.~Mut) +
    labs(y = name) +
    theme_classic() +
    theme(axis.title.x = element_blank(),
          axis.line = element_blank(),
          axis.text = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          strip.placement = "outside",
          strip.background = element_blank(),
          strip.text = element_text(size = 20),
          legend.text = element_text(size = 20),
          legend.title = element_text(size = 20),
          panel.border = element_rect(colour = "black", 
                                      fill = NA, 
                                      size = 1),
          plot.margin = unit(c(0,0,0,1.5), "lines")) +
    scale_fill_gradient(limits = c(0, maxFreq),
                        low = 'white', 
                        high = 'black',
                        breaks = c(100,250,500),
                        guide = guide_legend(title = 'Variant\ncount',
                                             direction = 'vertical'))
return(plt)
}
```

@@

merged_regression_unmasked$strict_mask <- "Pass strict mask"
merged_regression_masked$strict_mask <- "Fail strict mask"

@@

to_plot <- merged_regression %>%
           dplyr::filter(pvalue_glm_filt < 1 | Adjusted_Log10p > 2)

@@

p_comp
```
```{r}
#missing in Mafessoni
p <- to_plot %>%
  dplyr::filter(strict_mask == paste0("Pass strict mask (",nrow(merged_regression_unmasked),")"))

m_maf <- p %>%
           dplyr::filter(pvalue_glm_filt == 1 & Adjusted_Log10p > 2)

#missing in ours
m_us <- p %>%
           dplyr::filter(pvalue_glm_filt < 1 & Adjusted_Log10p < 2)

#present in both
both <- p %>%
           dplyr::filter(pvalue_glm_filt < 1 & Adjusted_Log10p > 2)

@@

#missing in Mafessoni
f <- to_plot %>%
  dplyr::filter(strict_mask == paste0("Fail strict mask (",nrow(merged_regression_masked),")"))

m_maf <- f %>%
           dplyr::filter(pvalue_glm_filt == 1 & Adjusted_Log10p > 2)

#missing in ours
m_us <- f %>%
           dplyr::filter(pvalue_glm_filt < 1 & Adjusted_Log10p < 2)

#present in both
both <- f %>%
           dplyr::filter(pvalue_glm_filt < 1 & Adjusted_Log10p > 2)

@@

m_maf <- to_plot %>%
           dplyr::filter(pvalue_glm_filt == 1 & Adjusted_Log10p > 2)

#missing in ours
m_us <- to_plot %>%
           dplyr::filter(pvalue_glm_filt < 1 & Adjusted_Log10p < 2)

#present in both
both <- to_plot %>%
           dplyr::filter(pvalue_glm_filt < 1 & Adjusted_Log10p > 2)
